a and generators

### 2022-05-03 documentos/pce.tex
multiindex
comentarios
Errare humanum est.

(b), (c) and (d) correspond to the identity map, dephasing channel, and 
total depolarization, respectively, 

@@

In order to present and develop the $N$ qubit case, it is useful 
to introduce 
the so-called \textit{Pauli strings}, defined as 
\begin{equation}
\sigma_{\vec \alpha}=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $\vec \alpha$ denotes a vector index $\qty(\alpha_1,\ldots,\alpha_N)$
\janote{revisar si en el resto del artículo siempre le llamamos a $\valpha$
`vector index'. A veces le poníamos `multi-index'}
and $\alpha_i=0,1,2,3$. These hermitian operators form an orthogonal 
basis in the space of operators acting on $N$ qubits. In fact, 
$\tr \sigma_{\vec \alpha} \sigma_{\vec \alpha'}=2^N\delta_{\valpha \valpha'}$
and 
$\tr \sigma_{\vec \alpha}= 2^{N}\delta_{\vec\alpha \vec 0}$.
% 
% Thus, given $N$ and the fact that $\tr
% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
% \textit{Pauli basis},
% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.

>>>>

(b), (c) and (d) correspond to the identity map, completely dephasing channel,
and 
complete depolarization, respectively, 

@@

In order to present and develop the $N$ qubit case, it is useful 
to introduce 
the so-called \textit{Pauli strings}, defined as 
\begin{equation}
\sigma_{\vec \alpha}=\sigma_{\alpha_1}\otimes \sigma_{\alpha_2} \otimes \dots \otimes \sigma_{\alpha_N},
\label{eq:pauli_strings}
\end{equation}
where $\vec \alpha$ denotes a multi-index $\qty(\alpha_1,\ldots,\alpha_N)$
and $\alpha_i=0,1,2,3$. These hermitian operators form an orthogonal 
basis in the space of operators acting on $N$ qubits. In fact, 
$\tr \sigma_{\vec \alpha} \sigma_{\vec \alpha'}=2^N\delta_{\valpha \valpha'}$
and 
$\tr \sigma_{\vec \alpha}= 2^{N}\delta_{\vec\alpha \vec 0}$.
% 
% Thus, given $N$ and the fact that $\tr
% \sigma_{\vec \alpha}=\delta_{\vec\alpha,\vec 0} 2^{N}$, it is clear that the
% basis $\left\{ 2^{N/2} \sigma_{\vec \alpha} \right\}$ is orthonormal in
% $\mcB(\hilbert_{2^N})$. The case with $N=1$ corresponds to the well-known
% \textit{Pauli basis},
% $1/\sqrt{2} \left\{ \one, \sigma_x,\sigma_y,\sigma_z \right\}$.
